---
title: "Quantitative data plan analysis"
subtitle: "REDRESS"
author: "Lucas Sempe / Yan Ding"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
```{r xaringan-themer, include=FALSE, warning=FALSE}

knitr::opts_chunk$set(echo = FALSE, dpi = 300, out.width = '500px',
                      warning = F, message = F,
                      fig.showtext = TRUE)

library(xaringanthemer)
style_mono_accent(
  base_color = "#1c5253",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Fira Mono"),
  header_h1_font_size = "2.0rem",
  footnote_font_size = "0.3em",
)
source("graphs.R")

```

# REDRESS Case Management of skin NTDs across Liberia

**Objective**

Describe magnitudes and trends of case management done by REDRESS during 1 year.

**Empirical strategy**

1) Descriptive statistics

- 


---
# Impact of REDRESS 

**Objective**

Identify the causal impact of REDRESS project (what can be attributed to REDRESS) in terms of increase of case detection, treatment and management.

**Empirical strategy**

2) Difference-in-differences (known also as Controlled Before-After)

- Detect differences between pre and post intervention between 2 groups (intervention and control counties)

$$\text{Y}= \alpha{_0} + \beta_{1} \text{Time} + \beta_{2} \text{REDRESS} + \beta_{3} \text{Time}*\text{REDRESS} + \text{County} +  \text{covars} + \epsilon$$
where $\text{Y}$ is the number of cases of skin NTDs **detected**, **treatment** and **managed**.

--

**Data**

- Primary data collection (Health Facility tool page 1 from ledger) and DHIS2

- Analysis done at health facilities level

---
# Impact of REDRESS 

- Difference-in-differences (known also as Controlled Before-After)

```{r, fig.showtext = TRUE}

p + theme_xaringan()

```

---
# Impact of REDRESS 


**ACTION: $\text{Ys}$ have to be defined by MoH/REDRESS team and preregistered**

**Risks and limitations**

- Lack of statistical power due to small number of observations or lack of variance on data

 - ***Including more health facilities (from all counties) will provide stronger statistical power***

  - ***If case management started in different periods, this can be addressed on the [empirical strategy](https://www.sciencedirect.com/science/article/pii/S0304407620303948?via%3Dihub)***

  - ***Transit to [Bayesian difference-in-differences](https://www.tandfonline.com/doi/full/10.1080/2330443X.2019.1626310)***

- Multiple comparisons

 - **Use false discovery rate (FDR) procedures**
 
- Not finding statistical differences / mixed results

  -**Focus on qualitative data to understand reasons and processes**

---
# Health facilities (i)

- descriptive analysis of NTDs cases at health facility level (& comparison over time) 
 
    - differences between case-management and control districts in terms of number and type and management of cases
    
    - interactive map with number and type of cases per Health facility
---


# Health facilities (ii)

- descriptive analysis of lab cases at health facility level (& comparison over time) 

    - per disease
    
    10.1093/cid/ciy197
  
  
---

# Health facilities (iii)

- incentives (Rozi)
  
  
---
# Health workers (i)

- Descriptive analysis (& comparison over time) of health workers at health facility level
  
    - sex, age, income, education
    
    - supervision
    
    - stigma
    
    - social distancing
 
  **differences between health workers**   

---
# Health workers (ii)

- Comparison between Likert scales and percentage scales in Health workers

    - supervision
    - stigma
    - social distancing
    - satisfaction

  **differences between sex, level of education, age** 
    
  **differences between case-management and control districts**

---

training before after

---

# Patients and carers (i)

- Descriptive analysis (& comparison over time) of *patients* at health facility level

    - sociodemographics: sex, age, wealth, education
    - disease 
    - PHQ-9 and GAD-7
    - SARI Stigma

  **correlations between PHQ, GAD and SARI**


10.1093/trstmh/trw065 #interesting paper on delay of diagnosis and hospitalisation

**can we get data from hospitalizations?**

https://bmjopen.bmj.com/content/11/8/e046125.long
---


# Patients and carers (ii)

- Descriptive analysis of *caregiver* information (& comparison over time) 
    
    - sociodemographics: sex, age, wealth, education
    - burden of care (time, tasks, ) 
    - PHQ-9 and GAD-7
    - SARI Stigma
    
  **correlations between PHQ, GAD and SARI**
    
    https://doi.org/10.1371/journal.pntd.0009030
    
---

# Patients and carers (iii)

- Comparison between Likert scales and percentage scales in patient and carers

    - PHQ-9
    - GAD-7
    - SARI Stigma

  **differences between sex, level of education, age** 

https://doi.org/10.1371/journal.pntd.0009454

---

# Patients and carers (iv)

- Descriptive analysis of *patient* satisfaction (& comparison over time) 

  **differences between sex, level of education, age** 
   
---

# Health workers / finance

- Descriptive analysis (& comparison over time) of CHAs/CHVs time and expenses

  **differences between districts or counties?** 

---

# Patients and carers / finance (i)

- Descriptive analysis: How much people spend with NTDs out-of-pocket expenditure (& comparison over time)?   (from patients' survey)

    - expenditure type (medication, transportation, faith healers, hospitalisation food)

- Descriptive analysis: How much people spend on faith healers (& comparison over time)? (from patients' survey)

    - expenditure type
    
    10.1136/bmjopen-2017-020113
    
---

# Patients and carers / finance (ii)

- Descriptive analysis: How much people spend with mental health expenditure (& comparison over time)?   (from patients' survey)

    - expenditure type (medication, transportation, faith healers, hospitalisation food)

---

# Health finance (i)

- Cost of interventions

    - out-of-pocket costs (patients tool)
    - estimation of time/cost (health worker tool)
    - costs of interventions (MoH/ACT/REDRESS - documents and interviews): case management, lab, mental health, training

**Cost benefit analysis**

---

# Health finance (ii)

- Issues with procurement, corruption, information flow, bureaucracy

**Qualitative** (plan to be developed)

---

# Health finance (iii)

- Systematic review of financing of SSSDs


---

# Training (i)

- Impact of training?

