---
title: "Quantitative data plan analysis"
subtitle: "REDRESS"
author: "Lucas Sempe / Yan Ding"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
```{r xaringan-themer, include=FALSE, warning=FALSE}

knitr::opts_chunk$set(echo = FALSE, dpi = 300, out.width = '500px',
                      warning = F, message = F,
                      fig.showtext = TRUE)

library(xaringanthemer)
style_mono_accent(
  base_color = "#1c5253",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Fira Mono"),
  header_h1_font_size = "2.0rem",
  footnote_font_size = "0.3em",
  base_font_size = "20px",
  text_font_size = ".85rem"
)
source("graphs.R")

```
# Data Availability 

--

.pull-left[
**SOURCE** <br>

ROUTINE DATA <br>

HEALTH FACILITY <br>

LAB <br>

PATIENT <br>

HEALTH WORKER <br>

TRAINING
]

--

.pull-right[
**STATUS**<br> 

OK <br>

OK <br>

NOT ENOUGH OBSERVATIONS (n=?) <br>

NOT ENOUGH OBSERVATIONS (n=6) <br>

OK <br>

TO BE COLLECTED
]

---
# Magnitudes of REDRESS Case Management

--

**Objective**

1) Describe magnitudes and trends over 1 year of case management done by REDRESS in 6 districts.

--

**Empirical strategy**

1a) Descriptive statistics

- number of cases detection, management and treatment
  - trends in time
  - comparison between counties/districts

1b) Interactive map with number and type of cases per Health facility

--

**Data**

- Health Facility survey tool (primary data collection) and HMIS

**Sample**

- 6 districts within 3 counties
- all surveyed and non-surveyed health facilities in those areas

---
# Impact of REDRESS 

--

**Objective**

2) Identify the causal impact of REDRESS project (what can be attributed to REDRESS) in terms of increase of case detection, treatment and management.

3) Identify the causal impact of the REDRESS non-cash award (what can be attributed to REDRESS) in terms of increase of case detection, treatment and management.

---
# Impact of REDRESS 

--

**Empirical strategy**

2) Case management

- Difference-in-differences (known also as Controlled Before-After)

- Detect differences between pre and post intervention between 2 groups (intervention and control counties)

$\text{Y}= \alpha_{0} + \beta_{1} \text{Time} + \beta_{2} \text{REDRESS} + \beta_{3} \text{Time}*\text{REDRESS} + \beta_{4}\text{County} + {...} + \beta_{n}\text{covars} + \epsilon$

where $\text{Y}$ is the number of cases of skin NTDs **detected**, **treatment** and **managed**, such as:

  -	number of cases clinically diagnosed at each health facility level

  -	number of suspected patients referred from community

  - of active case search through household visit

  -	number of cases diagnosed in the early stages of the diseases (E.g.: Leprosy G0D, Buruli Cat 1, Lymphedema Stage 1 & 2)

The analysis is done at the health facility level.

---
# Impact of REDRESS 

--

**Empirical strategy**

3) Non-cash award

  - Difference-in-differences (known also as Controlled Before-After)
  
 - Detect differences between pre and post intervention between 2 groups (intervention and control counties)

$$\text{Y}= \alpha{_0} + \beta_{1} \text{Time} + \beta_{2} \text{Non-CASH} + \beta_{3} \text{Time}*\text{Non-CASH} + \text{County} +  \text{covars} + \epsilon$$
where $\text{Y}$ is the number of cases of skin NTDs and $\text{Non-CASH}$ corresponds to those facilities that were part of the scheme. 

The analysis is done at the health facility level. 

  
---
# Impact of REDRESS 
--

**Data**

- HMIS

- Non-cash award intervention

--

**Sample**

- Treatment: 3 counties (Lofa, Grand Gedeh, Margibi)

- Control: 4 counties (Nimba, Bomi, Sinoe, Cape Mount)

- all health facilities in those areas

.center[***Is there any difference in terms of SAMPLE between REDRESS and non-cash awards?***

If ***YES***, we would be able to isolate the effects of both.

IF ***NO***, the empirical strategy changes and we assess the role of non-cash awards as a contribution to the effects of REDRESS.
]

---
# Impact of REDRESS 

--

- Difference-in-differences (known also as Controlled Before-After)

```{r, fig.showtext = TRUE}

p + theme_xaringan()

```

---
# Health workers

--

**Objective**

4) Describe attitudes towards NTDs, supervision and  tasks of health workers over time

  
5) Explore association between changes on attitudes towards NTDs (job satisfaction & motivation), supervision and  tasks of health workers over time

--

**Empirical strategy**

4) Descriptive statistics / Item Response Theory models

- Disaggregation by sex, type of health worker position, counties, districts, etc.

- Analysis over time

- Comparison between Likert scales and percentage scales in Health workers


---
# Health workers

--


**Empirical strategy**


5) Hierarchical linear modelling / Structural equation modelling

- Associations between: 

  - supervision (scales and raw variables)
    
  - stigma (scales and raw variables)
    
  - social distancing (scales and raw variables)
    
    - satisfaction (scales and raw variables)

- Fixed effects at health facility, district and county levels
    
- Before-after intervention: 

$$\text{Y}= \alpha_{0j} + \beta_{1j} \text{Time}_{ij} +  {...} + \beta_{nj} \text{covars}_{ij}  + \epsilon_{ij}$$
where $\text{Y}$ is the number of cases of skin NTDs **detected**, **treatment** and **managed**. Random intercepts and slopes are allowed at health facility level (if it converges).

---
# Health workers

--

**Data**

- Health workers survey tool (primary data collection)

--

**Sample**

- Treatment: 3 counties (Lofa, Grand Gedeh, Margibi)

- health workers surveyed within facilities 

---

# Health finance

--

**Objective**

6) Estimate the cost of REDRESS interventions

--

**Empirical strategy**

6) Cost unit and cost centre analysis

  - estimation of size of workforce
  
  - estimation of health workers time and salaries
  
  - estimation of intervention inputs:
  
    - case management
    
    - lab
    
    - mental health
    
    - training
  
---

# Health finance

--

**Data**

- Document revision from costs of interventions (MoH/ACT/REDRESS - documents and interviews)
  
- HMIS

- Health facility tool

- Health worker tool

--

**Sample**

- Treatment: 3 counties (Lofa, Grand Gedeh, Margibi)

- health facilities and health workers surveyed

---
# Training

--

**Objective**

7) Describe pre- and post- training knowledge and comparison over time

  
8) Explore association between changes on training knowledge and attitudes towards NTDs, supervision and  tasks of health workers over time

9) Explore association between changes on training knowledge and number of case detection, management and treatment

--

**Empirical strategy**

7) Descriptive statistics

- Disaggregation by sex, type of health worker position, counties, districts, etc.

- Analysis over time


---
# Training

--

**Empirical strategy**

8) Associations of knowledge assessment and: 

    - supervision
    
    - stigma
    
    - social distancing
    
    - satisfaction
    
    - number of cases


- Hierarchical linear modelling / Structural equation modelling

- Fixed effects at health facility, district and county levels
    
$$\text{Y}= \alpha_{0j} + \beta_{1j} \text{Time}_{ij} + 
 \beta_{2j} \text{Assessment}_{j} + \beta_{3j} \text{Time}_{j}*\text{Assessment}_{j}    +
{...} + \beta_{nj} \text{covars}_{ij}  + \epsilon_{ij}$$

where $\text{Y}$ is the scales for **supervision**, **stigma**, **social distancing** and **satisfaction**. Random intercepts and slopes are allowed at health facility level (if it converges).

---

# Training

--

**Empirical strategy**

9) Before-after gain in assessment: 

Hierarchical linear modelling / Structural equation modelling

- Fixed effects at health facility, district and county levels
    
- Before-after intervention: 

$$\text{Y}= \alpha_{0j} + {...} + \beta_{nj} \text{covars}_{ij}  + \epsilon_{ij}$$

where $\text{Y}$ is the difference between test results as in $\Delta = Test_{End} - Test_{Baseline}$. Random intercepts and slopes are allowed at health facility level (if it converges).

---
# Training

--

**Data**

- Pre and post training survey (primary data collection)

- Health Facility survey tool (primary data collection) and HMIS

- Health worker survey tool (primary data collection)

--

**Sample**

- Treatment: 3 counties (Lofa, Grand Gedeh, Margibi)

- health workers surveyed


---
# Risks and limitations

- Lack of statistical power due to small number of observations or lack of variance on data

 - ***Including more health facilities (from all counties) will provide stronger statistical power***

  - ***If case management started in different periods, this can be addressed on the [empirical strategy](https://www.sciencedirect.com/science/article/pii/S0304407620303948?via%3Dihub)***

  - ***Transit to [Bayesian difference-in-differences](https://www.tandfonline.com/doi/full/10.1080/2330443X.2019.1626310)***

- Multiple comparisons

 - **Use false discovery rate (FDR) procedures**
 
- Not finding statistical differences / mixed results

  - **Focus on qualitative data to understand reasons and processes**
  
  - **Focus on further descriptive analysis**

---

# What we can't do due to current data availability

- Analysis on patients and carers (stigma, mental health, PHQ-9, GAD-7)

- Out-of-pocket costs 

- Analysis on lab work

# Questions

- Analysis on Faith healers?

- Additional available secondary data (MoH, international agencies)

- **ACTION: $\text{Ys}$ have to be defined by MoH/REDRESS team and preregistered**





